\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-07-31 paper.qmd
Update Figure 8 title.

```{r}
#| echo: false
#| fig-cap: "Various plots to help assess best bin start position, number of bins, low density bin and large edge removal. Both (a) and (c) show MSE, against number of bins and standardised count, while (a) also shows the change in MSE for different $q$. A good benchmark value for these parameters is when the MSE drops and then flattens out. Plot (b) shows the distribution of stadardised counts of hexagons. Plot (d) shows the distribution of $2\\text{-}D$ Euclidean distances between bin centroids, with a good benchmark value for removing large edges would being the distance that shows the first large increase."
#| label: fig-param-scurve
#| out-width: 100%
#| fig-width: 12
#| fig-height: 10
#| fig-pos: H

>>>>

```{r}
#| echo: false
#| fig-cap: "Various plots to help assess best hexagon bin parameters, thresholds to remove low density bins and large edges. Both (b) and (c) show MSE, against number of bins along the x-axis and standardised count. A good benchmark value for these parameters is when the MSE drops and then flattens out. Plot (a) shows the distribution of stadardised counts of hexagons. Plot (d) shows the distribution of $2\\text{-}D$ Euclidean distances between bin centroids, with a good benchmark value for removing large edges would being the distance that shows the first large decrease."
#| label: fig-param-scurve
#| out-width: 100%
#| fig-width: 12
#| fig-height: 10
#| fig-pos: H

### 2024-07-31 paper.tex
Updated Figure 8
Update Figure 8 title.

The default number of bins \(b=b_1\times b_2\) is computed based on the
sample size, by setting \(b_1=n^{1/3}\), consistent with the
Diaconis-Freedman rule \citep{freedman1981}. The value of \(b_2\) is
determined analytically by \(b_1, q, r_2\). Values of \(b_1\) between
\(2\) and \(b_1 = \frac{n}{2}\) are allowed. FIG XXX(b) shows the effect
of different choices of \(b_1\) on the MSE of the fitted model. XXX Are
you showing \(b_1\) or \(b\) here???? \(b\)

@@

\caption{\label{fig-param-scurve}Various plots to help assess best bin
start position, number of bins, low density bin and large edge removal.
Both (a) and (c) show MSE, against number of bins and standardised
count, while (a) also shows the change in MSE for different \(q\). A
good benchmark value for these parameters is when the MSE drops and then
flattens out. Plot (b) shows the distribution of stadardised counts of
hexagons. Plot (d) shows the distribution of \(2\text{-}D\) Euclidean
distances between bin centroids, with a good benchmark value for
removing large edges would being the distance that shows the first large
increase.}

>>>>

The default number of bins \(b=b_1\times b_2\) is computed based on the
sample size, by setting \(b_1=n^{1/3}\), consistent with the
Diaconis-Freedman rule \citep{freedman1981}. The value of \(b_2\) is
determined analytically by \(b_1, q, r_2\). Values of \(b_1\) between
\(2\) and \(b_1 = \frac{n}{2}\) are allowed.
Figure~\ref{fig-param-scurve} (b) shows the effect of different choices
of \(b_1\) on the MSE of the fitted model.

@@

\caption{\label{fig-param-scurve}Various plots to help assess best
hexagon bin parameters, thresholds to remove low density bins and large
edges. Both (b) and (c) show MSE, against number of bins along the
x-axis and standardised count. A good benchmark value for these
parameters is when the MSE drops and then flattens out. Plot (a) shows
the distribution of stadardised counts of hexagons. Plot (d) shows the
distribution of \(2\text{-}D\) Euclidean distances between bin
centroids, with a good benchmark value for removing large edges would
being the distance that shows the first large decrease.}
